---
title: "RJAGS"
author: "Anita Kurm"
date: "2/17/2020"
output: html_document
---

# Week 2 
Chicken sexer and learning (Theta is a parameter representing skill level)

Set-up
```{r}
pacman::p_load(R2jags)
set.seed(666)
#setwd("/Users/anitakurm/Desktop/Masters 2nd semester/Cognitive-Modelling/Module 1") 
```


## Model 1: fixed theta model
simulating binary choices and checking if it's right
output is an array of 0 (wrong) and 1 (right)
Model is a for loop, randomly generating a hit or a miss at a time
 #G is determined by/distributed as fixed theta

```{r}
#make an array of 0s that we can populate later with agent's guesses
#dimensionality of 1 (row), 100 (columns), array(0, c(2,100)) - 2 rows 100 columns, check ?array
Gfixed <- array(0, c(100))

#make a fixed parameter
theta <- .7

#number of trials
ntrials <- 100

#our model
  #G is determined by/distributed as some process, hence arrow and not equal sign!!
  #r - randomly sample, binom - from binomial distribution (discrete)¨
  #1 trial at a time 
for (t in 1:ntrials) {
  
  Gfixed[t] <- rbinom(1,1,theta) 
  
}

#How many successes there are?
sum(Gfixed)
```
<- approximately proportionate to the fixed theta!


JAGS: 
model{

  theta ~ dbeta(1, 1) (alpha - success, beta - misses, so 1-1 is basically no information)
  for (t in 1:ntrials) {
   G[t] ~ dbinom(theta)  G at every trial is distributed binomially with a parameter theta (that is fixed)
  }
}

### Run inference for the fixed model using the fixed data

```{r}
G <-  Gfixed

#look in the workspace for G, ntrials - things to put into the model
data <- list("G", "ntrials")

#parameters to keep track of - things to get out of the model (we are trying to recover parameters here)
params <- c("theta")


#jags
samples <- jags(data, inits = NULL, params,  
                model.file = "chick.txt",
                n.chains = 3, n.iter = 5000, n.burnin = 1000, n.thin = 1) #you average over the sampling chains, 3 is normal, don't go below 3

#remember to hit return in the console
traceplot(samples)

#get the theta parameter out
X <-  samples$BUGSoutput$sims.list$theta
plot(X)

#the posterior for theta
plot(density(X))
```
<- THIS IS YOUR CONCLUSION


Rhat - not much bigger than 1 means chains are sufficiently randomly overriding each other 


## Model 2: learning model
We need a fixed starting theta and a fixed alpha (learning rate)
Theta will be updated in every trial according to the learning rule

Jags is not sequential
```{r}
#arrays to be populated with guesses and updated theta after learning
Glearn <- array(0, c(100))
theta <- array(0, c(100))

#fixed parameters (learning rate alpha and starting skill level theta)
alpha <- .05
theta1 <- .5

ntrials <- 100

#Define first trial
theta[1] <- theta1
Glearn[1] <-  rbinom(1, 1, theta[1])

#model
for (t in 2:ntrials) {
  #theta in every trial is determined by the previous trial's theta in the power of 1 over 1+learning rate ('the learning rule')
  
  theta[t] <- theta [t-1]^(1/(1 + alpha))
  #update guess
  Glearn[t] <- rbinom(1, 1, theta[t])
}

#Glearn - you can see by the end only ones, 
Glearn

sum(Glearn)

#see theta over time (the learning curve)
plot(theta)
```


### Retrieve theta from the learning data
```{r}
G <-  Glearn

data <- list("G", "ntrials")
params <- c("theta", "theta1", "alpha")


#jags
samples <- jags(data, inits = NULL, params,  
                model.file = "chick_learn.txt",
                n.chains = 3, n.iter = 5000, n.burnin = 1000, n.thin = 1) #you average over the sampling chains, 3 is normal, don't go below 3

#remember to hit return in the console
#traceplot(samples)

#get the theta parameter out
X <-  samples$BUGSoutput$sims.list$theta
plot(X)

#the posterior for theta
plot(density(X))
```

