---
title: "Module 3"
author: "Anita Kurm"
date: "3/11/2020"
output: html_document
---


# Set-up
```{r}
pacman::p_load(extraDistr, R2jags, tidyverse)
source("/Users/anitakurm/Desktop/Masters 2nd semester/Cognitive-Modelling/Module 1/quick_n_clean_plots.R")

# maximum aposterior function:
jag_map <- function(param_samples){
  dens <- density(param_samples)
  return(dens$x[dens$y == max(dens$y)])
}

```


# PVL model

Generarte task environment: Iowa gambling task
4 decks, the person is told both what they won but also what they lost

```{r}
#----------------------generate task environment

#Bad frequent
A_R <-  rep(100, 10) #reward for deck A: 10 rewards of 100kr (100 kr every time you choose Deck A)
A_L <- c(rep(-250, 5), rep(0,5)) #5 big losses, 5 no loss


#Bad infrequent
B_R <-  rep(100, 10) #reward for deck B: 10 rewards of 100kr if you choose Deck A
B_L <- c(rep(-1250, 1), rep(0,9))   #1 very big loss, 9 no loss

#Good frequent
C_R <-  rep(50, 10) #reward for deck A: 10 rewards of 100kr if you choose Deck A
C_L <- c(rep(-50, 5), rep(0,5))

#Good infrequent
D_R <-  rep(50, 10) #reward for deck A: 10 rewards of 100kr if you choose Deck A
D_L <- c(rep(-250, 1), rep(0,9))

A <-c()
for (i in 1:10){ A <- (append(A, A_R + sample(A_L)))} #take reward and loss, shuffle and add up all combinations, get 10*10 = 100 outcomes for decks 

B <-c()
for (i in 1:10){ B <- (append(B, B_R + sample(B_L)))}

C <-c()
for (i in 1:10){ C <- (append(C, C_R + sample(C_L)))}

D <-c()
for (i in 1:10){ D <- (append(D, D_R + sample(D_L)))}

payoff <- cbind(A,B,C,D)
```


```{r}
#build PVL-Delta model
w <- 2 #loss aversion parameter 
A <- .5  #shape of the utility function, has to be between  0 and 1

theta <- .01 #response consistency in the softmax function
a <- .1 #learning rate, between 0 and 1

ntrials <- 100


source("PVL.R")
PVL_sims <- PVL(payoff, ntrials, w, A, a, theta=3)

par(mfrow=c(2,2))
plot(PVL_sims$Ev[,1])
plot(PVL_sims$Ev[,2])
plot(PVL_sims$Ev[,3])
plot(PVL_sims$Ev[,4])

```


## Parameter recovery

```{r}
x <- PVL_sims$x
X <-  PVL_sims$X

data <- list("x", "X", "ntrials")
params <- c("w", "A", "theta", "a")

samples <- jags.parallel(data, inits = NULL, params,
                model.file = "PVL_jags.txt",
                n.chains = 3, n.iter = 5000, n.burnin = 1000, n.thin = 1)
```




```{r}
  

######Just extra, to see what propsect theory parameters do



#---- plot prospect theory function for GAINS
  A <- .1
  objective_val <- seq(1,100, 1)
  subjective_util <- objective_val^A #prospect theory
  plot(objective_val, subjective_util)
  
  
  
  #---- plot prospect theory function for LOSS
  w <-  2 #loss aversion parameter
  A <- .1
  objective_val <- seq(1,100, 1)
  subjective_util <- -w*(objective_val^A) #prospect theory
  plot(objective_val, subjective_util)
```



# ORL model
The Outcome Representation Learning model
– Haines, Vassileva, & Ahn, 2018


Generarte task environment: Iowa gambling task
4 decks, the person is told both what they won but also what they lost

```{r}
#----------------------generate task environment

#Bad frequent
A_R <-  rep(100, 10) #reward for deck A: 10 rewards of 100kr (100 kr every time you choose Deck A)
A_L <- c(rep(-250, 5), rep(0,5)) #5 big losses, 5 no loss


#Bad infrequent
B_R <-  rep(100, 10) #reward for deck B: 10 rewards of 100kr if you choose Deck A
B_L <- c(rep(-1250, 1), rep(0,9))   #1 very big loss, 9 no loss

#Good frequent
C_R <-  rep(50, 10) #reward for deck A: 10 rewards of 100kr if you choose Deck A
C_L <- c(rep(-50, 5), rep(0,5))

#Good infrequent
D_R <-  rep(50, 10) #reward for deck A: 10 rewards of 100kr if you choose Deck A
D_L <- c(rep(-250, 1), rep(0,9))

A <-c()
for (i in 1:10){ A <- (append(A, A_R + sample(A_L)))} #take reward and loss, shuffle and add up all combinations, get 10*10 = 100 outcomes for decks 

B <-c()
for (i in 1:10){ B <- (append(B, B_R + sample(B_L)))}

C <-c()
for (i in 1:10){ C <- (append(C, C_R + sample(C_L)))}

D <-c()
for (i in 1:10){ D <- (append(D, D_R + sample(D_L)))}

payoff <- cbind(A,B,C,D)
payoff <- payoff/100
```



## Set all six free parameters
```{r}
alpha_rew <- .2  
alpha_pun <- .5

beta_f <- -2 #weight of frequency - values for bF less than or greater than 0 indicate that decision mak- ers prefer decks with low or high win frequency
beta_per <- 1.5 #weight of perseverance <-  values for bP less than or greater than 0 indicate that decision makers prefer to switch or stay with recently chosen decks, respectively

K <- 1  #a decay parameter controlling how quickly decision makers forget their past deck choice
theta <- 1 #in in the softmax function

ntrials = 100
```


## Simulate ORL data

```{r}
source("ORL.R")
ORL_sims <- ORL(payoff, ntrials, alpha_rew, alpha_pun, beta_f, beta_per, K, theta)

plot(ORL_sims$x)

par(mfrow=c(2,2))
plot(ORL_sims$V[,1])
plot(ORL_sims$V[,2])
plot(ORL_sims$V[,3])
plot(ORL_sims$V[,4])


par(mfrow=c(2,2))
plot(ORL_sims$Ev[,1])
plot(ORL_sims$Ev[,2])
plot(ORL_sims$Ev[,3])
plot(ORL_sims$Ev[,4])


par(mfrow=c(2,2))
plot(ORL_sims$PS[,1])
plot(ORL_sims$PS[,2])
plot(ORL_sims$PS[,3])
plot(ORL_sims$PS[,4])

par(mfrow=c(2,2))
plot(ORL_sims$p[,1])
plot(ORL_sims$p[,2])
plot(ORL_sims$p[,3])
plot(ORL_sims$p[,4])


```


## Parameter Recovery
TO DO: more simularions with different parameters
```{r}
x <- ORL_sims$x
X <-  ORL_sims$X

data <- list("x", "X", "ntrials")
params <- c("alpha_rew", "alpha_pun", "beta_f", "beta_per", "K", "theta")

samples <- jags.parallel(data, inits = NULL, params,
                model.file = "ORL_jags.txt",
                n.chains = 3, n.iter = 5000, n.burnin = 1000, n.thin = 1)

#inferred params

inferredK <- jag_map(samples$BUGSoutput$sims.list$K)
plot_actual_predicted(K, inferredK)

inferred_arew <- jag_map(samples$BUGSoutput$sims.list$alpha_rew)
plot_actual_predicted(alpha_rew, inferred_arew)

inferred_apun <- jag_map(samples$BUGSoutput$sims.list$alpha_pun)
plot_actual_predicted(alpha_pun, inferred_apun)

inferred_betaf <- jag_map(samples$BUGSoutput$sims.list$beta_f)
plot_actual_predicted(alpha_rew, inferred_betaf)

inferred_betaper <- jag_map(samples$BUGSoutput$sims.list$beta_per)
plot_actual_predicted(alpha_rew, inferred_betaper)

inferred_theta <- jag_map(samples$BUGSoutput$sims.list$theta)
plot_actual_predicted(alpha_rew, inferred_theta)
```



# VSE model
Value plus Sequential Exploration (VSE) model

## Task environment
```{r}
RA <- A
RA[A < 0] = 100
RB <- B
RB[B < 0] = 100
RC <- C
RC[C <= 0] = 50
RD <- D
RD[D < 0] = 50

# extract losses from reward trials
LA <- A
LA[A > 0] = 0
LA[LA < 0] = -250
LB <- B
LB[B > 0] = 0
LB[LB < 0] = -1250
LC <- C
LC[C == 0] = -50
LC[LC > 1] = 0
LD <- D
LD[D > 0] = 0
LD[LD < 0] = -250

R <- cbind(RA,RB,RC,RD)
L <- cbind(LA,LB,LC,LD)

Loss_matrix <- abs(L)
Gain_matrix <- R

```


## Set all five free parameters

```{r}

theta = 0.01  #value sensitivity parameter - bound between 0 and 1
delta = 0.4 #decay parameter, bound between 0 and 1
alpha = 0.5 #learning rate bound between 0 and 1
phi = 0.8  #exploration bonus - unbounded, positive means agent is attracted by unchosen recently decks, negative means agent favors familiar decks
beta = 0.9 #inverse temperature bound between 0 and 5


ntrials = 100
```


## Simulate data
```{r}
source("VSE.R")
VSE_sims <- VSE(Gain_matrix, Loss_matrix, ntrials, theta, delta, alpha, phi, beta)

plot(VSE_sims$x)
plot(VSE_sims$value)
plot(VSE_sims$Explore[,1])
plot(VSE_sims$Explore[,2])
plot(VSE_sims$Explore[,3])
plot(VSE_sims$Explore[,4])

plot(VSE_sims$x)
plot(VSE_sims$Explore[,1])
plot(VSE_sims$Exploit[,1])


plot(VSE_sims$x)
plot(VSE_sims$Explore[,2])
plot(VSE_sims$Exploit[,2])
```



